Brandt et al. example: equivalent & not significant

### 2017-11-08 NSEQ_Brandt_Example.Rmd

```{r include = FALSE}
library(TOSTER)

@@

# Calculate critical effect (d): smallest effect orig. study had the power to detect
t.crit = qt(1-.05/2, (orig.N-2))
d.crit = t.crit*sqrt((1/(orig.N/2)) + 1/(orig.N/2))

Brandt <- TOSTtwo(m1=rep.m1, m2=rep.m2, sd1=rep.sd1, sd2 = rep.sd2, n1 = rep.n1, n2=rep.n2, low_eqbound_d = -d.crit, high_eqbound_d = d.crit, var.equal = FALSE)
```

@@

As an example, Banerjee, Chatterjee, & Sinha (2012) reported that participants who had been asked to describe an unethical deed from their past judged the room to be darker than participants who had been asked to describe an ethical deed ($M_{unethical}= `r orig.m1`$, ${SD}_{unethical}= `r orig.sd1`$, $M_{ethical}=`r orig.m2`$, ${SD}_{ethical}=`r orig.sd2`$, $t(`r orig.df`)= `r orig.t`$, $p= `r orig.p`$, $d= `r orig.d`$). A close replication by Brandt, IJzerman, & Blanken (2014) found no significant effect ($t(`r rep.df`)=`r rep.t`$, $p=`r rep.p`$, $d=`r rep.d`$).  The smallest effect the original study could have detected is $d_{crit}= `r round(t.crit, 2)` \sqrt { \frac { 1} {`r orig.N/2`} + \frac { 1} {`r orig.N/2`} }=`r round(d.crit, 2)`$. Using this as our SESOI for a TOST with Welch's t-test for independent samples --- resulting in equivalence bounds of ${\Delta}_L=`r round(-d.crit, 2)`$ and ${\Delta}_U=`r round(d.crit, 2)`$ --- we indeed find that the effect reported by the replication study is equivalent, $t(`r round(Brandt$TOST_df, 2)`)=`r round(min(Brandt$TOST_t1, Brandt$TOST_t2), 2)`$, $p=`r round(max(Brandt$TOST_p1, Brandt$TOST_p2), 3)`$.

```{r, fig.width=6}
TOSTtwo(m1=rep.m1, m2=rep.m2, sd1=rep.sd1, sd2 = rep.sd2, n1 = rep.n1, n2=rep.n2, low_eqbound_d = -d.crit, high_eqbound_d = d.crit, var.equal = FALSE)
```

[^1]: This will typically, although not always, correspond to the effect size the study had $50\%$ power to detect. This procedure will thus result in effect sizes that are substantially larger than the ones obtained using the small telescopes approach, which gives the effect size a study had $33\%$ power to detect.

>>>>

```{r include = FALSE}
library(TOSTER)
library(pwr)

@@

# Calculate small telescopes effect (d) effect orig. study had 33% power to detect
d.33 <- (pwr.t.test(n = orig.N/2, d = NULL, sig.level = 0.05, power = 0.33, type = "two.sample", alternative = "two.sided"))$d

Brandt <- TOSTtwo(m1=rep.m1, m2=rep.m2, sd1=rep.sd1, sd2 = rep.sd2, n1 = rep.n1, n2=rep.n2, low_eqbound_d = -d.33, high_eqbound_d = d.33, var.equal = FALSE)
```

@@

Banerjee, Chatterjee, & Sinha (2012) reported that participants who had been asked to describe an unethical deed from their past judged the room to be darker than participants who had been asked to describe an ethical deed ($M_{unethical}= `r orig.m1`$, ${SD}_{unethical}= `r orig.sd1`$, $M_{ethical}=`r orig.m2`$, ${SD}_{ethical}=`r orig.sd2`$, $t(`r orig.df`)= `r orig.t`$, $p= `r orig.p`$, $d= `r orig.d`$). A close replication by Brandt, IJzerman, & Blanken (2014) found no significant effect ($t(`r rep.df`)=`r rep.t`$, $p=`r rep.p`$, $d=`r rep.d`$). Following the small telescopes approach, we can calculate the effect size the original study had $33\%$ power to detect --- $d = `r round(d.33, 2)`$ --- and use this as our SESOI. If we run a TOST with Welch's *t*-test for independent samples and equivalence bounds of ${\Delta}_L=`r round(-d.33, 2)`$ and ${\Delta}_U=`r round(d.33, 2)`$, we indeed find that the effect reported by the replication study is statistically equivalent, $t(`r round(Brandt$TOST_df, 2)`)=`r round(min(Brandt$TOST_t1, Brandt$TOST_t2), 2)`$, $p=`r round(max(Brandt$TOST_p1, Brandt$TOST_p2), 3)`$.
